An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-15 EconGrowth.Rnw
Updated to-do list on the paper.

\item Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model.

@@

@@

<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
cdeGridGraph(countryAbbrev="ZA", energyType="Q")
@

>>>>

\item{Heun: Rearrange the panels on the CD gamma grid search graph}
\item{Heun: Change the strip to transparent on the CD gamma grid search graph}
\item{Heun: Get full country names into the CD gamma grid search graph}
\item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
\item{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}
\item{Heun: Remove cdeGridGraph function}

@@

\item{\st{Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model}}

@@
